I first would like to thank my advisor, Toyoko Orimoto. I am sincerely grateful to have had an advisor who has been on my side every step of the way during the course of my PhD, and who clearly prioritized my well-being above all else. Toyoko always enthusiastically encouraged me to follow my heart when it came to choosing research projects and activities, which led to me enjoying my research. I would not have had such a meaningful and fruitful PhD experience if it were not for her. 

I would also like to thank the HH to WW$\gamma\gamma$ analysis team: Mingshui Chen, Peiran Li, Petr Mandrik, Badder Marzocchi, Fabio Monti, Ram Krishna Sharma, Sergei Slabospitskii, Junquan Tao, Joshuha Thomas-Wilsker, Chu Wang, and Jin Wang. One of the many fortunate circumstances which made my PhD experience special was the opportunity to lead a physics analysis working group. I am grateful to have had that opportunity, through which I learned from everybody in the group. 

During my PhD, I was also very fortunate to be part of the wonderful CMS ECAL community. While I am grateful for all of the many people who I have learned from in this group, I would like to express special thanks to Giacomo Cucciati, David Petyt, and Davide Valsecchi. Giacomo was always incredibly kind and willing to thoroughly answer my countless questions about ECAL DAQ, and was a great partner in crime at ECAL Run Coordination. The experience I have gained working with David has been invaluable and an important part of my PhD. David was also willing to answer my endless questions, in this case about ECAL TPG, and always took the time to share his insightful perspective and feedback as the projects we worked on developed over time. Finally, whether it was through Italian lessons or ECAL trigger discussions, Davide and I always had \textit{fun} with what we discussed. This was an absolutely essential aspect of our work. Keeping things fun kept us interested in collaborating over our multi-year projects. 

I also want to thank Tanvi, Chad and Andrew for keeping me company while we were under lockdown during the pandemic. All of the meaningful conversations, support, silly jokes, and laughter kept me sane.  

Finally, I want to thank my parents for encouraging me to pursue a PhD in the first place, and for believing in me more than I believed in myself. 