\section{Simulated samples} \label{sec:Phase_II_Samples}

Because this analysis is a projection study of the prospects for \wwgg and \ttgg searches as the future HL-LHC and upgraded CMS detector, the samples used in the analysis are exclusively simulation. 

As was done for the Run 2 analysis, signal Monte Carlo $gg\rightarrow HH$ samples are generated using \textsc{Powheg v2} \cite{Nason:2004rx, Frixione:2007vw, Alioli:2010xd, Heinrich:2019bkc} 
at next-to-leading order (NLO) in QCD including the full top quark mass dependence with the SM parameters. 

Subsequent decays of the Higgs boson pairs into WW or $\tau\tau$ and a pair of photons are implemented using \textsc{Pythia 8.212} \cite{Sjostrand:2014zea}. \wwgg samples are generated separately for each final state in \wwgg. 
For \ttgg signal samples, all possible decays for taus are allowed.

As the process signature remains the same for both the Run 2 and Phase II analyses, the expected background signatures also remain the same. The analysis is affected by backgrounds from single Higgs boson production and by non-resonant backgrounds with continuum $m_{\gamma\gamma}$ spectra.
The event generator \textsc{Madgraph5\_amcatnlo} \cite{Alwall:2014hca, Artoisenet:2012st} with the FxFx merging scheme \cite{Frederix:2012ps} was used for the generation of the background from SM single Higgs boson production, including  gluon-gluon fusion (ggH), vector-boson fusion (VBFH), associated production with a Z or W boson (VH)  and associated production with a top quark pair (ttH). The additional single Higgs production mode of top quark associated production (tHq) is also included, and was generated using \textsc{Madgraph} version-2.7 at LO. 

The continuum background contribution comes from various SM processes. Most of the dominant backgrounds
across all the final states are due to the $\gamma\gamma+$jets processes that are 
modeled with the \textsc{Sherpa} v.2.2.1 generator \cite{Bothmann:2019yzt}.
$\gamma+$jets, QCD-induced processes and WW processes are modeled with the PYTHIA 8 \cite{Sjostrand:2014zea} generator.

Drell Yan and W production processes in association with photons and jets are modeled using \textsc{Madgraph5} version-2.7 at LO. 
Finally, the $t\bar{t}$ process is generated using \textsc{Powheg} v2, and $t\bar{t}W$, $t\bar{t}\gamma$, $t\bar{t}\gamma\gamma$, Z$\gamma$ are modeled using \textsc{Madgraph5\_amcatnlo} \cite{Alwall:2014hca,Artoisenet:2012st,Frederix:2012ps}.

For these simulation samples, all are simulated with the Phase-2 upgraded CMS detector geometry using \textsc{Delphes} fast simulation  
with average pile-up of 200 interactions and at 
$\sqrt{s}=14$ TeV, the expected data-taking conditions at the HL-LHC. 